Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more edits

In our problem, the answer is not as clear. On the one hand, since we are
interested in the ringdown part of the signal, it is natural to use the
final mass $M_f$ to compute $\Lambda_{\rm EFT}$.
%
On the other hand, one may argue that the modified gravity theory under study
should be able to predict a full inspiral, merger, and ringdown of the black
hole binary before we can even make such a test, and thus the same, more conservative choice
$\gm = m_2$ should be used.
%
Here we adopt an agnostic view to this question and consider \emph{both} masses, $m_2$ and $M_f$, to
determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
yield to different interpretations of the results of our parameter estimations.

@@

\subsection{cubic effective-field-theory of general relativity}
\label{sec:results_ceft}

@@

\subsection{quartic effective-field-theory of general relativity}
\label{sec:results_qeft}

>>>>

In our problem, the answer is not as clear. On the one hand, since we are
interested in the ringdown part of the signal, it is natural to use the
final mass $M_f$ to compute $\Lambda_{\rm EFT}$.
%
On the other hand, one may argue that the modified gravity theory being
consideration should be able to predict a full inspiral, merger, and ringdown
of the black hole binary before we can even make such a test, and thus the
same, more conservative choice $\gm = m_2$ should be used.
%
Here we adopt an agnostic view to this question and consider \emph{both} masses, $m_2$ and $M_f$, to
determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
yield to different interpretations of the results of our parameter estimations.

@@

\subsection{Cubic Effective-Field-Theory of General Relativity}
\label{sec:results_ceft}

@@

\subsection{Quartic Effective-Field-Theory of General Relativity}
\label{sec:results_qeft}
